\newpage
\begin{center}
  \LARGE
  % \begin{singlespace}
  % 	\titleEn \\[0.5cm]
  % \end{singlespace}

  % \begin{singlespace}
  % \begin{tabular}{r l}
  %   Student : & \studentEn \\
  %   Advisor : & Dr. \advisorEn \\[0.5cm]
  % \end{tabular}
  % \end{singlespace}

  % \begin{singlespace}
  % \instituteEn{} of\\ \universityEn \\[0.5cm]
  % \end{singlespace}
    
  Acknowledegment \\[0.5cm]	
\end{center}

\normalsize 
I would like to thank the following people, without whom I would not have been able to complete this research, and without whom I would not have made it through my master's degree!
\begin{enumerate}
  \item The NCRL Lab. at National Yang Ming Chiao Tung University, especially to my advisor Dr. Teng-Hu Cheng, whose insight and knowledge into the subject matter steered me through this research.
  \item Eason Huang, who showed me how to efficiently debug the hardware problem during the experiment and offered a lot of opinions about the design of the experiment.
  \item Lioujgay, who carefully heard the problem that I faced, and gave me other useful perspectives to my research.
  \item Huan Boa, who helped me check the bugs in the algorithm, and discussed the detail in UKF, including the model and observability.
  \item TH Liu, who taught me how to arrange the structure of my code and fixed the simulation environment conflict. He also gave me the faith to face the problem.
  \item JoJo Chen, who was good at coordinate transformations, and always willing to figure out the coordinate promblem with me.
  \item Dr. Wang, who was my experiment partner. By our experiment related communication, I often received much helpful information and inspiration. Also, he shared the workload with me, which speeded up the progress of my research work.
  \item Others in the lab, who have supported me when I was down, and put up with my temper for the past two years of study.
  \item My family, who have been giving me all the care, trust and support.
\end{enumerate}